\Title

### 2021-07-01 manuscript/content.tex
Tweaks to figures
Use RbBy for synthetic data since it's diverging (and seismic is a bit
too saturated at the ends). Make the random/sequential comparison single
column by plotting convergence on the same plot. Add xlabel to the
histogram in australia residuals.

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Results of interpolating the airborne synthetic survey with
        gradient-boosted equivalent sources with overlapping windows being
        iterated in random order (a and b), and with overlapping windows being
        iterated in sequential order (c and d).
        (a and c)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data produced
        gradient-boosted.
        (b and d)~Root-mean squared error of the residuals after each iteration
        of the gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure*}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figs/eql-boost-airborne.pdf}
    \caption{
        Interpolation error for gradient-boosted equivalent sources using
        randomized (a) and sequential (b) window order.
        (a and b)~Pseudo-color maps of the differences between the target grid
        and the interpolated synthetic airborne survey data.
        (c)~Root-mean squared error after each iteration of the
        gradient-boosting algorithm.
}
\label{fig:eql-boost-airborne}
\end{figure}
